---
title: "HW8 Association Rules"
author: "Aaron"
date: "July 6, 2016"
output: 
  html_document: 
    highlight: haddock
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Instrunctions: 

First, install the package arules

```{r message=F}

library(arules)
library(dplyr)
library(ggplot2)

```

Second, load the data set using the following command

```{r}

grd <- read.transactions("http://fimi.ua.ac.be/data/retail.dat", format="basket")

```

Third, run the following commands and interpret the results

```{r}
itemFrequencyPlot(grd,support=.1)
```

```{r}
itemFrequencyPlot(grd,support=.2)
```

```{r}
itemFrequencyPlot(grd,support=.3)
```


```{r}
summary(grd)
```

```{r}
# inspect(grd)  #you will have to stop the listing manually
```


Create the rules object using apriori

```{r}

grdar <- apriori(grd,parameter=list(supp=.05,conf=.5))

inspect(grdar)

```

Now that you have rules,…
Find a few interesting rules
Tell me something you learned from interpreting the rules

#### Interesting Rules

*Rule no.1*: `{41}    => {48} 0.10228897 (S) 0.6034125 (C)  1.2625621 (L)` 

Itme `41` happens (end up in the grocery buyer's basket) about 10% of the time, and once that happens, 76% of the time, item `39` is there too, this prediction is about 20% better than random guess. 

*Rule no.2*: `{38,39} => {48} 0.06921349 (S) 0.5898502 (C)  1.2341847 (L)`
Itme `38 and 39` happens (end up in the grocery buyer's basket) about 6% of the time, and once that happens, 59% of the time, item `48` is there too, this prediction is about 24% better than random guess. 

